`flippant` -- An `R` package for the automated  analysis of dithionite

### 2015-09-17 inst/manuscript/manuscript.rmd
Roearganize structure, including a data processing section;

#Installation, Input Requirements and Main Features
##Installation
`flippant` has been integrated into the `bioconductor` collection of tools for 
biomedical data analysis [@huber_orchestrating_2015] and is thus installable and
loadable as follows from within a functioning `R` environment:
```{r eval = FALSE}
source("http://bioconductor.org/biocLite.R")
biocLite(pkgs = "flippant")
library(flippant)
```
The package depends on the following, automatically satisfied extensions to `R`
base functionality: `r flippant_dependencies`

##Input Data
To analyse raw data stemming from dithionite scramblase assays, `flippant` 
requires for each data point information as the path to the 
fluorometer-generated spectrum, the amount of protein used to reconstitute 
proteoliposomes, the volume used in the assay before and after addition of 
dithionite (to calculate a volume correction factor), the amount of lips 
present (to calculate a proteine to phospholipid ratio or PPR) etc. The 
following function generates a spreadsheet program-compatible tab-delimited 
`ASCII` template including column names, commentary, expected data type and the 
default used when ommited, supporting the user in providing the data needed in 
one table row per data point.
```{r echo = FALSE, comment = ""}
make.usage.section("scramblaseAssayInputTemplate", env = asNamespace("flippant"))
```
The application agnostic tab-delimited format must be maintained for the 
completed table, which is subjected to extensive input checks when read by 
`flippant`.

>>>>

#Installation
`flippant` has been integrated into the `bioconductor` collection of tools for 
biomedical data analysis [@huber_orchestrating_2015] and is thus installable and
loadable as follows from within a functioning `R` environment:
```{r eval = FALSE}
source("http://bioconductor.org/biocLite.R")
biocLite(pkgs = "flippant")
library(flippant)
```
The package depends on the following, automatically satisfied extensions to `R`
base functionality: `r flippant_dependencies`

#Input Data and Data Processing
To analyse raw data stemming from dithionite scramblase assays, `flippant` 
requires for each data point information as the path to the 
fluorometer-generated spectrum, the amount of protein used to reconstitute 
proteoliposomes, the volume used in the assay before and after addition of 
dithionite (to calculate a volume correction factor), the amount of lips 
present (to calculate a proteine to phospholipid ratio or PPR) etc. The 
following function generates a spreadsheet program-compatible tab-delimited 
#Main Features
##Template Generation for Data Input
The following function generates a spreadsheet program-compatible tab-delimited 
`ASCII` template including column names, commentary, expected data type and the 
default used when ommited, supporting the user in providing the data needed in 
one table row per data point.
```{r echo = FALSE, comment = ""}
make.usage.section("scramblaseAssayInputTemplate", env = asNamespace("flippant"))
```
The application agnostic tab-delimited format must be maintained for the 
completed table, which is subjected to extensive input checks when read by 
`flippant`.
